---
title: "Principal Component Analysis"
output: html_document
---

Detailed data attached at the end

```{r echo=FALSE}
student=read.csv("student.csv")
fertilization=read.csv("fertilization.csv")
fertilization=fertilization[,-1]
fertilization1=scale(fertilization[,-4])
```

```{r}
## principal components analysis
student.pr=princomp(~X1+X2+X3+X4, data=student, cor=TRUE) 
## summary
summary(student.pr, loadings=TRUE)
##  scores
predict(student.pr)
##  screepplot
screeplot(student.pr,type="lines")
biplot(student.pr)
```

## Principal component regression analysis using [psych](https://cran.r-project.org/web/packages/psych/) package: A brief example
For more details of Parallel Analysis, see [Factor Retention Decisions in Exploratory Factor Analysis: A Tutorial on Parallel Analysis](https://www.researchgate.net/publication/235726204_Factor_Retention_Decisions_in_Exploratory_Factor_Analysis_A_Tutorial_on_Parallel_Analysis)

### Linear model: vif值很大, 说明存在**严重多重共线性**

```{r}
lmo.sol=lm(y~., data=fertilization)
summary(lmo.sol)
library(car)
vif(lmo.sol)
```

### Principal components analysis
判断主成分个数的方法：  

- 先验经验和理论知识  
- 事先确定的累计贡献率阈值  
- 根据Kaiser-Harris准则: 保留特征值大于1的主成分  
- 进行平行分析: 基于多次模拟数据矩阵的特征值均值来选取主成分  

```{r message=FALSE, warning=FALSE}
library(psych)
```
```{r}
fa.parallel(fertilization1, fa = "pc", n.iter = 100, 
            show.legend = FALSE, main = "Scree plot with parallel analysis")
```

按照parallel analysis的结果, 选取一个主成分, 并作出主成分与原变量的关系图

```{r}
fertilization.pr=principal(fertilization1, nfactors=1, rotate="none")
fertilization.pr
fa.diagram(fertilization.pr)
```

建立主成分回归模型并计算原方程系数

```{r echo=FALSE}
fertilization.pr1=princomp(~., data=fertilization[,-4], cor=T)

#### principal components regression ##############
pre=predict(fertilization.pr1)
fertilization$F1=pre[,1]
```
```{r}
lm.sol=lm(y~F1, data=fertilization)
summary(lm.sol)
```
```{r echo=FALSE}
#### transformation ###############################
beta=coef(lm.sol)
A=loadings(fertilization.pr1)
x.bar=fertilization.pr1$center
x.sd=fertilization.pr1$scale
if(length(beta)==2){
  coef=(beta[2]*A[,1])/x.sd
}
if(length(beta)>=3){
  coef=beta[2]*A[,1]
  for(i in 2:(length(beta)-1)){
    coef=coef + beta[i+1]*A[,i]
  }
  coef=coef/x.sd
}
beta0=beta[1]-sum(x.bar*coef)
c(beta0, coef)
```

## Appendix: datasets

```{r echo=FALSE}
library(knitr)
kable(student, caption="student")
kable(fertilization, caption="fertilization")
```
