---
title: "假设性检验"
output: html_document
---

Reference: 应用多元统计分析 高惠璇 Charter 3  
Detailed data attached at the end

```{r echo=FALSE}
source("Normial Test.r")
female.data=read.csv("female.csv")
japan=read.csv("Economy_Japan.csv")
usa=read.csv("Economy_USA.csv")
health=read.csv("health.csv")
```

## 单总体均值检验

```{r}
mu0=c(4, 50, 10)
Sigma0=var(female.data)
## var known 
result1=mu.test.known(female.data, mu0, Sigma0, alpha=0.05)
result1
## var unknown 
result2=mu.test(female.data, mu0)
result2
```

## 两总体等方差均值检验

```{r}
result3=two.mu.test(japan, usa)
result3
```

## 多总体等方差均值检验 -- 多元方差分析

```{r}
result4=multi.mu.test(health, 3)  ##3 groups 
result4
```

## 单总体正态分布方差检验

```{r}
Sigma0=matrix(c(100,10,0,6,100,-5,0,0,4),nrow=3)
result5=var.test(female.data, Sigma0)
result5
```

## 多总体正态分布方差检验

```{r}
result6=multi.var.test(health, 3) 
result6
```

## 多总体正态分布均值方差同时检验

```{r}
result7=multi.mean.var.test(health, k=3)
result7
```

## 多元正态独立性检验

```{r echo=FALSE}
library(MASS)
set.seed(086)

times=1000
n=200
mu=c(1, 0)
Sigma <- matrix(c(0.5,0,0,0.5), nrow = 2, byrow = TRUE)
```

Simulation: Run the function for `r times` times, each time generating `r n` 
data which have NID(`r mu`; `r Sigma`), and proceeding independence test.
Record t-value and p-value each time. If p-value is significant, rejects 
the null hypothesis, i.e. the test fails. The average of the number of failures 
is calculated to evaluate the test performance.

```{r echo=FALSE}
p=rep(0,times)
t=rep(0,times)
pi=rep(0,times)
```

```{r}
for(i in 1:times)
{
  mydata <- as.data.frame(mvrnorm(n, mu, Sigma))
  subvector <- c(1,2)
  k=2 # divided into k sub-vector to test independence
  re=norm.independent.test(mydata, subvector, k)
  # If p-value is significant, rejects the null hypothesis, 
  # i.e. the test fails.
  t[i]=re$t
  pi[i]=re$p.value
  if(re$p.value<0.05)
  {
    p[i]=1
  }
}
sum(p) ## total fail times
t[18]  ## t-value of the 18th result
pi[18] ## p-value of the 18th result
```

Example:

```{r}
subvector <- c(1,2,3)
k=3
result8=norm.independent.test(female.data, subvector, k)
result8
```

## Appendix: datasets

```{r echo=FALSE}
library(knitr)
kable(female.data, caption="female.data")
kable(japan, caption="japan")
kable(usa, caption="usa")
kable(health, caption="health")
```